Model

### 2023-05-09 Experiment_4/model.Rmd
- update Y-axis scale in model plots

  # Create a relative measure of competence that allows to compare across
  # different numbers of choice options. 
  # This measure varies from 0 = chance to 1 = definitely right. 
  # We use min-max scaling, with min = 1/options and max = 1.
  data <- data %>% 
    mutate(relative_competence = (competence - 1/options) / (1 - 1/options)
           )

@@

## Results by varying choice options and sample size function

@@

### a

@@

  # plot for accuracy
  plot_accuracy <- ggplot(d,
                          aes(x = constellation, y = average_accuracy, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Accuracy") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1))

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y = average_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1))

@@

### b

@@

```{r}
plot_results <- function(data, variable = options) {

@@

plot_results(data_3_options)
plot_results(data_3_sample, variable = sample)

@@

```{r}
data_3 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 3)

data_10 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 10)

data_100 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 100)

data_2 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 2)
```

```{r}
plot_results(data_3)
plot_results(data_10)

data_3 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

```{r}
data_10 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

```{r}
data_2 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

@@

```{r}
test <- simulate_single_population(population = 999, sample = 3, options = 3)
plot_results(test)
```

>>>>

  # Create a relative measure of competence that allows to compare across
  # different numbers of choice options. 
  # This measure varies from 0 = random chance to 1 = definitely right. 
  # We use min-max scaling, with min = 1/options and max = 1.
  data <- data %>% 
    mutate(relative_competence = (competence - 1/options) / (1 - 1/options)
           )

@@

## Function for varying choice options and sample size function

@@

### a) Plot various populations

@@

  # plot for accuracy
  plot_accuracy <- ggplot(d,
                          aes(x = constellation, y = average_accuracy, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Accuracy") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y = average_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

@@

### b) Plot varying sample options

@@

```{r}
plot_results_vary <- function(data, variable = options) {

@@

plot_results_vary(data_3_options)
plot_results_vary(data_3_sample, variable = sample)

@@

```{r}
data_3 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 3)
```

```{r}
data_3 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

@@
